Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-10 constantRate/ConstCompFuzzExt-crypto.tex
small edits to proof of 3.6
gone through section 3

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

\section{Reusable Construction for Sources with High-Entropy Samples}
\label{sec:sampling}
Let $w$ be a string of symbols (over an arbitrary alphabet) $w=w_1\dots w_\gamma$. The construction first chooses a random fuzzy extractor output $r$. It then samples a random subset of blocks $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$.  This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. Let $\sample_{\gamma, \eta}(\cdot)$ denote an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$.
Let $\eta$ be a parameter, and $\mathcal{O}$ be an obfuscator for the family of digital lockers with $\kappa$-bit outputs.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma,\eta}( \lambda_i)$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, \lambda_i$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w'=w_1',..., w_\gamma', p)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

This construction can use the na\"{i}ve sampler that takes truly random samples. If desired, public randomness may be substantially decreased by using more sophisticated samplers. (See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)

\begin{theorem}
\label{thm:sampling}
Let $\mathcal{Z}$ be an alphabet.  Let $n$ be a security parameter.  Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma =\Omega(n)$.  Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$, and let $c> 1$ be a constant and $\ell$ be such that $\ell = n^c$.  Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\leq -\frac{(c-1)}{2} \frac{(\gamma-\eta)\log n}{\eta} = o(\gamma)\\
\delta &= e^{-n}
\end{align*}
\end{theorem}

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
\end{lemma}

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.  Thus, given sufficiently strong reusability we achieve the following result:

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.  The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.  Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
\bnote{say more here?}
\end{proof}

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

@@

\section{Construction for Sources with High-Entropy Marginals}

\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

\subsection{Positive Examples}
\label{sec:positive ex}
We begin with the case of independent blocks.

@@

\subsection{Negative Examples}
\label{sec:negative ex}
Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.  This is not always the case.  Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.

@@

\section{Analysis of \consref{cons:sampling}}
\label{sec:analysis sampling}
\subsection{Security}
The proof of security for \consref{cons:sampling} uses the definition of block unguessable sources~(\defref{def:block guessable}).  This definition is adaptive and discussed in \apref{sec:characterize}.
We show the security of \consref{cons:sampling}:
\begin{itemize}
\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
\item The outputs $V_1,..., V_\ell$ are a block unguessable source.  This is made formal in the following corollary:
\begin{corollary}
\label{cor:v are unguessable}
Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}. Take any $q=\poly(n)$.  For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block source.
\end{corollary}
\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable source.
\end{itemize}

\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]

\lnote{I need to check this}
Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable source.  The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .  Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block source.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.

Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
\[
| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
\[I_{v_1,..., v_\ell, r}(x, i) =
\begin{cases}
r & v_i = x\\
\perp & \text{otherwise.}
\end{cases}\]
By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $R$ and $U$.
\begin{lemma}
\label{lem:sim cannot distinguish samp}
$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
\begin{lemma}
\label{lem:codewords in I close samp}
Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then,
\[
\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}.
\]
\end{lemma}
\begin{proof}
Recall that for all $j$, $\Hav(V_j | View(S))\geq \alpha''$.  The only information about the correct value of $r$ is contained in the query responses.  When all responses are $\perp$ the view of $S$ is identical when presented with $r$ or $u$.  We now show that for any value of $r$ all queries return $\perp$ with probability $1-2^{-\alpha''}$.  Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha'')}$.

 When there is a response other than $\perp$ for some $j$ this means that there is no remaining min-entropy in $V_j$.  If this occurs with over $2^{-\alpha''}$ probability this violates the block unguessability of $V$~(\defref{def:block guessable}).  By the union bound over the indices $j$ the total probability of a response other than $\perp$ is at most $\ell 2^{-\alpha''}$. Thus, for all $r, u$ the statistical distance is at most $\ell 2^{-\alpha''}$.  This concludes the proof of \lemref{lem:codewords in I close samp}.
\end{proof}
By averaging over all points in $\zo^\kappa$ we conclude that
\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
\end{proof}

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
\begin{align*}
\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
\end{align*}
This is a contradiction and completes the proof of \lemref{lem:samp unguess}.
\end{proof}

%\end{proof}
\subsection{Correctness}
\label{sec:sampling errors}

Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.
\begin{align*}
\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
\end{align*}
We then have the probability that all $v_i\neq v_i'$ as:
\begin{align*}
\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
\end{align*}
This completes the proof of \lemref{lem:sampling errors}.
\end{proof}

\section{Analysis of \consref{cons:first construction}}
\label{sec:construction analysis}
\subsection{Security}
Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.  However, security is more complicated, the main difficulty is that the definition of block unguessable sources~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.  This means we must limit our indistinguishable distribution to blocks that are difficult to guess.  Security is proved via the following lemma:

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

\section{Reusable Construction for Sources with High-Entropy Samples}
\label{sec:sampling}

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$(\eta, \subsetEntropy)$-high-entropy samples} if $\Hav(w_{j_1}, \dots, w_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

A distribution obtained by applying short-output condensers multiple times to a single sample from a high-entropy source (e.g., via random projections) will have this property, because the outputs of the condensers will be contain fresh entropy as long as the total amount of entropy in the source is not exceeded
(by a simple conditional entropy argument---each subsequent element in the sequence $w_{j_1}, \dots, w_{j_\eta}$ will extract fresh entropy as long as fresh entropy remains conditioned on the previous elements).

\paragraph{The Construction}
The construction first chooses a random $r$ to be used as the output of the fuzzy extractor. It then samples a random subset of symbols $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$ (We present and analyze the construction with uniformly random subsets; however, if necessary, it is possible to substantially decrease the required public randomness and the length of $p$ by using more sophisticated samplers. See~\cite{goldreich2011sample} for an introduction to samplers.) This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source with $(\eta, \subsetEntropy)$-high-entropy samples, where each $W_j$ is over $\mathcal{Z}$.  Let $\ell$ be a parameter, to be determined later. 
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for the family of digital lockers with $\kappa$-bit outputs. Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Choose uniformly random distinct $1\le j_{i, 1},..., j_{i, \eta}\le \gamma$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, (j_{i, 1},..., j_{i, \eta})$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w'=w_1',..., w_\gamma', p = p_1\dots p_\ell)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, (j_{i, 1},..., j_{i, \eta})$.
\item Set $v_i' = w_{j_{i, 1}}',..., w_{j_{i, \eta}}'$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter, $\mathcal{Z}$ be an alphabet, and $\gamma, \subsetEntropy$, and $t$ be functions of $n$, as follows.  Let $\mathcal{W}$ be a family of sources over $\mathcal{Z}^\gamma$ with $(\eta, \subsetEntropy)$ high-entropy samples for $\subsetEntropy = \omega(\log n)$. Let $t$ be such that $\left(1-\frac{t}{\gamma-\eta}\right)^\eta>1/p(n)$ for some positive polynomial $p$. Then it there exists $\ell = \poly(n)$ such that for any
$s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $\left (\epsilon_{sec}, s_{sec}\right)$-hard with negligible error.
\end{theorem}

 Correctness follows immediately: for any given $i$, the probability that $v'_i=v_i$ is at least $1/p(n)$. By choosing $\ell$ sufficiently bigger than $1/p(n)$, we guarantee that for at least one $i$,  $v'_i=v_i$ with all but negligible probability
(indeed, because the $\ell$ samples are independent, the probability this does not happen is at most $(1-1/p(n))^\ell \le e^{-\ell/p(n)}$, using $1+x \le e^x$).

Security follows from obfuscation and is analyzed in \apref{sec:analysis sampling}.

\paragraph{Any sublinear error-rate can be supported if most symbols in a sample contribute entropy.}
The requirement on $t$ can be expressed as $\eta \log  \left(1-\frac{t }{\gamma-\eta}\right) = O (\log n)$. Using $\ln (1+x)\approx x$ and relying on $O$ to absorb any 
constant factor involved in this approximation and the switch from $\ln$ to $\log$, we get $\eta \frac{t }{\gamma-\eta} = O(\log n)$. If $t$ is sublinear in $\gamma$
 (and $\eta$ is no more than a constant fraction of $\gamma$), then $t/(\gamma-\eta)$ is subconstant, and therefore it is possible to satisfy this requirement on $t$ while simultaneously maintaining $\eta = \omega (\log n)$, which implies $\subsetEntropy = \omega(\log n)$ as long as most symbols in a sample of size $\eta$ contribute a constant amount of entropy each.

\paragraph{More Errors than Entropy?}
The amount of entropy in $W$ need not exceed $\subsetEntropy$---thus, it can be as low as $\omega(\log n)$. Assuming $\gamma = n$, the number $t$ of errors may be any function in $o(n)$, and thus $\log |B_t| \ge t \log |Z|$ may far exceed $\Hoo(W)$.

\iffalse 
\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.
\end{lemma}
\fi

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input. Consider any $q = \poly(n)$ number of reuses.  For each fixed $i\in \{1,..., q\}$, we can treat the keys $r_1,\dots, r_{i-1}, r_{i+1}, \dots, r_q$ and the strings $p_1, \dots, p_q$ as auxiliary input to the obfuscation adversary. The result follows by simulatability of this adversary, using the same argument as the proof of Theorem~\label{thm:sampling} in \apref{sec:analysis sampling} (note that the simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations, which allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$).

  Thus, given sufficiently strong reusability we achieve the following result:

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ is an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}

\iffalse
\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

@@

\fi

\section{Construction for Sources with Sparse High-Entropy Marginals}
\label{sec:cor construction}
\lnote{stopped here; also need to reorder appendices}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

\subsubsection{Positive Examples}
\label{sec:positive ex}
We begin with the case of independent blocks.

@@

\subsubsection{Negative Examples}
\label{sec:negative ex}
Claims~\ref{cl:each block from single seed} and~\ref{cl:all blocks entropy} rest on there being no easy ``entry'' point to the distribution.  This is not always the case.  Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.

@@

\subsection{Security}
Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.  However, security is more complicated, the main difficulty is that the definition of block unguessable sources~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.  This means we must limit our indistinguishable distribution to blocks that are difficult to guess.  Security is proved via the following lemma:
